### 2013-07-22 docs/Jesse/Dissertation/H1DPG.tex
updating confusion, dissertation, and NS

%&pdflatex
\documentclass[final,leqno]{siamltex}
%\documentclass[10pt,onecolumn]{article}
\usepackage[top=2cm,bottom=3cm,left=3.5cm,right=3.5cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs}
\let\proof\relax 
\let\endproof\relax
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amscd}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage[normalem]{ulem}

\newcommand{\bs}[1]{\boldsymbol{#1}}

\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}

\newcommand{\tablab}[1]{\label{tab:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}

\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\snor}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\LRb}[1]{\left| #1 \right|}

\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\!\left[#1\right]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\def\etal{{\it et al.~}}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\Delta}
\let\grad\relax
\newcommand{\grad}{\nabla}
\newcommand{\curl}{\grad \times}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}

%\newtheorem{proposition}{Proposition}
%\newtheorem{corollary}{Corollary}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}

\newcommand{\G} {\Gamma}
\newcommand{\Gin} {\Gamma_{in}}
\newcommand{\Gout} {\Gamma_{out}}

\newtheorem{remark}{Remark}

\title{A minimum-residual finite element method for the convection-diffusion equation}
\author{Jesse Chan, John A. Evans}
\date{}
\begin{document}

\maketitle

\begin{abstract}
We present a minimum-residual finite element method for convection-diffusion problems in a higher order, adaptive, continuous Galerkin setting.  The method borrows concepts from both the Discontinuous Petrov-Galerkin (DPG) method by Demkowicz and Gopalakrishnan \cite{DPG2} and the method of variational stabilization by Dahmen et al.\ \cite{DahmenVariationalStabilization}, and it can also be interpreted as a variational multiscale method in which the fine-scales are defined through a dual-orthogonality condition.  A key ingredient in the method is the proper choice of norm used to measure the residual, and we present two alternatives which are observed to be robust in both convection and diffusion-dominated regimes.  Numerically obtained convergence rates are given in 2D, and benchmark numerical examples in all space dimensions are shown to illustrate the behavior of the method.
\end{abstract}

%\tableofcontents
%\begin{keywords}\end{keywords}
%\begin{AMS}\end{AMS}

@@

Our starting point is the minimization of some measure of error over a finite-dimensional space.  We begin by first introducing an abstract variational formulation 
\begin{equation}
\eqnlab{variationEq}
\left\{
  \begin{array}{l}
    \text{Given } l \in V^*, \text{ find } u \in U  \text{ such that} \\ 
    b(u,v) = l(v), \quad \forall v\in V,
  \end{array}
  \right.
\end{equation}
where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous bilinear form.  Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U^*$ and $V^*$ as the respective topological dual spaces.  Throughout the paper, we suppose the variational problem \eqnref{variationEq} to be well-posed in the inf-sup sense. We can then identify a unique operator $B:U\rightarrow V^*$ such that 
\[
\langle Bu,v\rangle_{V^* \times V} \coloneqq b(u,v), \quad u\in U, v\in V
\]
with $\LRa{\cdot, \cdot}_{V^*\times V}$ denoting the duality pairing between $V^*$ and $V$, to obtain the operator form of the our variational problem
\begin{equation}
\eqnlab{dualEq}
Bu = l \quad \text{in } V^*.
\end{equation}
We are interested in minimizing the residual over the discrete approximating subspace $U_h \subset U$
\[
u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h) \coloneqq \frac{1}{2}\|l-Bu_h\|_{V^*}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| l(v)- b(u_h,v)|^2}{\nor{v}_V^2}.
\]
For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.  If we define the problem-dependent \textit{energy norm} 
\[
\nor{u}_E \coloneqq \nor{Bu}_{V^*},
\]
then we can equate the minimization of $J(u_h)$ with the minimization of error in $\nor{\cdot}_E$.

The first order optimality condition for minimization of the quadratic functional $J(u_h)$ requires the G\^ateaux derivative to be zero in all directions $\delta u \in U_h$,
\begin{align}
\left(l-Bu_h,B\delta u\right)_{V^*} = 0, \quad \forall \delta u \in U,
\label{orthog}
\end{align}
which is nothing more than the least-squares condition enforcing orthogonality of error with respect to the inner product on $V$.

The difficulty in working with the first-order optimality condition~\eqref{orthog} is that the inner product $\LRp{\cdot,\cdot}_{V^*}$ cannot be evaluated explicitly.  However, we have that 
\begin{align}
\left(l-Bu_h,B\delta u\right)_{V^*} = \left(R_V^{-1}(l-Bu_h),R_V^{-1}B\delta u\right)_{V},
\label{rieszOrthog}
\end{align}
where $R_V: V\rightarrow V^*$ is the Riesz map mapping elements of a Hilbert space $V$ to elements of the dual $V^*$ defined by
\[
\LRa{R_Vv,\delta v}_{V^*\times V} \coloneqq \LRp{v,\delta v}_V.
\]
Furthermore, the Riesz operator is an isometry, such that $J(u_h) = \frac{1}{2}\nor{l-Bu_h}^2_{V^*} = \frac{1}{2}\nor{R_V^{-1}(l-Bu_h)}^2_{V}$.  Thus, satisfaction of~\eqref{rieszOrthog} is exactly equivalent to satisfaction of the original optimality conditions~\eqref{orthog}.

@@

Secondly, we need to enforce the orthogonality of the error in equation~\eqref{rieszOrthog}, which becomes
\begin{align*}
\LRp{e,R_V^{-1}B\delta u}_V &= 0, \quad \forall \delta u \in U_h\\
\Rightarrow \LRa{e,B\delta u}_{V\times V^*} &= b(\delta u, e) = 0.
\end{align*}
Putting these two conditions returns the symmetric saddle-point problem for $\LRp{e,u_h} \in V\times U_h$
\begin{align*}
\LRp{e,v}_V + b(u_h,v) &= l(v), \quad \forall v\in V\\
b(\delta u, e) &= 0, \quad \forall \delta u \in U_h.
\end{align*}
We note that, under the perspective of the minimization of $J(u_h)$, this system can be viewed as a constrained optimization problem for $e$, where $u_h$ are Lagrange multipliers enforcing satisfaction of the variational problem.

@@

This formulation was first introduced by Dahmen et al.\ in \cite{DahmenVariationalStabilization}, where $V_h$ was determined adaptively.  The method proceeded in two steps -- first, $V_h$ was set equal to $U_h$ on what we will define as the \textit{coarse mesh}.  Next, \textit{a posteriori} error estimators for $e$ (based on a specific choice of inner product $\LRp{\cdot,\cdot}_V$) were used to drive adaptivity to determine a fine-scale mesh on which $V_h$ was supported.  We choose a simpler representation -- if $U_h$ is represented by piecewise polynomials of order $p$, we set $V_h$ to be piecewise polynomials of order $p+\triangle p$.  We note that these two choices of discretization for $V$ are not mutually exclusive, and that novel choices for $V_h$ are likely the key to yielding computationally effective methods under this framework.  
\subsection{DPG optimal test function framework}

The DPG method was introduced by Demkowicz and Gopalakrishnan in 2009, and rapidly applied to a series of problems in computational mechanics \cite{DPG2,DPG3,DPG4,maxwellDPG,stokesDPG}.  Though the DPG method shares the same variational setting as Dahmen et al.\, each method followed very different approaches in implementation.  Recall the orthogonality of error~\eqref{rieszOrthog}; by defining the error representation function $e$ and undoing the Riesz map acting on $B\delta u$, we recovered a saddle point formulation.  However, it is possible to instead undo the Riesz map acting on the residual instead, to recover
\begin{align*}
\LRp{R_V^{-1}\LRp{l-Bu_h},R_V^{-1}B\delta u}_V &= 0, \quad \forall \delta u \in U_h\\
\Rightarrow \LRa{\LRp{l-Bu_h},R_V^{-1}B\delta u}_{V^*\times V} &= 0\\
\Rightarrow l\LRp{R_V^{-1}B\delta u}-b\LRp{u_h,R_V^{-1}B\delta u} &= 0
\end{align*}
If we define $v_{\delta u} \coloneqq R_V^{-1}B\delta u$, then we recover the original variational formulation with a nonstandard test space
\[
b(u_h,v_{\delta u}) = l(v_{\delta u}), \quad \forall \delta u \in U_h.
\]
The DPG method with optimal test functions was constructed under this perspective of minimization of $J(u_h)$.  While $v_{\delta u} \in V$ must still be solved for approximately, under the assumption of discontinuous test functions, this solve can be localized to a single element.\footnote{In practice, if $U_h(K) = P^p(K)$ is the space of polynomials of order $p$ over the element $K$, then the enriched space $V_h \subset V$ is chosen to be $V_h(K) = P^{p+\triangle p}(K)$, where $\triangle p \geq n$, and $d$ is the spatial dimension.}

@@

We begin again with the variational problem
\[
\LRa{Bu,v}_{V^*\times V} = \LRa{l,v}_{V^*\times V},
\]
where, as before, $B: U\rightarrow V^*$ is the operator form of $b(u,v)$, and $l \in V^*$ is the load.  Standard VMS techniques then decompose $U$ into a \textit{coarse scale} space $U_h$ and \textit{fine scale} space $U'$, such that the coarse and fine scales $u_h \in U_h \subset U$ and $u' \in U'$ are related through some yet-unspecified orthogonality condition.  Decomposing $u = u_h + u'$ gives 
\begin{align*}
u_h \in U_h, u' \in U', v \in V\\
\LRa{Bu_h,v}_{V^*\times V} + \LRa{Bu',v}_{V^*\times V} = \LRa{l,v}_{V^*\times V}
\end{align*}
where $U = U_h\oplus U'$.  We can now explicitly choose our orthogonality condition defining the fine scales and rewrite the above problem as 
\begin{align*}
u_h \in U_h, u' \in U, v \in V\\
\LRa{Bu_h,v}_{V^*\times V} + \LRa{Bu',v}_{V^*\times V} &= \LRa{l,v}_{V^*\times V}\\
\LRp{u',\bar{w}}_E &= 0, \quad \forall \bar{w} \in U_h,
\end{align*}
where $\LRp{u',\bar{w}}_E$ is defined through
\begin{align*}
\LRp{u',\bar{w}}_E = \LRp{Tu',T\bar{w}}_V\\
T:U\rightarrow V, \quad T \coloneqq R_V^{-1} B
\end{align*}
where $\LRp{v,\delta v}_V$ is an inner product on $V$ and $R_V$ is the Riesz map associated with this inner product.  DPG literature refer to $T$ as the \textit{trial-to-test} operator, which, given a basis function $\phi_i \in U_h$, returns the optimal test function for $\phi_i$ \cite{DPG2}.

If we define our fine-scale using the above orthogonality condition, we have that
\begin{align*}
\LRp{Tu',v}_V = \LRp{R_V^{-1}Bu',v}_V = \LRa{Bu',v}_{V^*\times V}\\
\LRp{u',\bar{w}}_E = \LRp{Tu',R_V^{-1}B\bar{w}}_V = \LRa{Tu',B\bar{w}}_{V\times V^*}
\end{align*}
and can now rewrite our above VMS formulation as 
\begin{align*}
u_h \in U_h, u' \in U, v \in V\\
\LRa{Bu_h,v}_{V^*\times V} + \LRp{Tu',v}_{V} &= \LRa{l,v}_{V^*\times V}\\
\LRp{Tu',B\bar{w}}_{V\times V^*} &= 0, \quad \forall \bar{w} \in U_h.
\end{align*}
The saddle point formulation of Section~\ref{sec:saddlePoint} can be interpreted as solving not for $u'$, but for $e\coloneqq Tu'$.  The discrete approximation then follows directly from setting $V \coloneqq V_h$, some finite-dimensional enriched space, which impacts the method only through the approximation of $Tu'$ and the construction of the Riesz map $R_V^{-1}$.

To summarize, the minimum-residual framework motivating both Dahmen's variational stabilization and Demkowicz and Gopalakrishnan's DPG method can be characterized as a VMS method under which 
\begin{itemize}
\item Orthogonality of $U_h$ and $U'$ is defined through a nonstandard \textit{energy inner product} (i.\ e.\ $\LRp{u',u_h}_E = 0$), and
\item A change of variables (i.\ e.\ solving for $Tu'$ instead of $u'$) symmetrizes the fine-scale contribution and overall system.
\end{itemize}

@@

Our first method is motivated by previous results for the DPG method in \cite{DPGrobustness}, which achieved good results through a modification of the test norm.  We set
\[
\nor{v}_{V,w}^2 \coloneqq \frac{L}{\LRb{\beta}}\nor{\sqrt{w}\beta\cdot \Grad v}_{\L}^2 + \epsilon\nor{\Grad v}_{\L}^2 + \alpha\nor{v}_{\L}^2,
\]
where $L = \LRb{\Omega}^{\frac{1}{d}}$ is the length measure of $\Omega$ in $d$ spatial dimensions, $\LRb{\beta} = \max_\Omega \nor{\beta}_{l^2}$, and we have introduced the scaling $\frac{L}{\LRb{\beta}}$ on the streamline diffusion term for unit consistency\footnote{In all problems considered, $\frac{L}{\LRb{\beta}} = O(1)$.}. $\alpha \geq 0$ is a user-specified constant with units of inverse time\footnote{In the case where $\alpha = 0$, the seminorm remains a norm due to equivalence with the $H^1$ seminorm, which is norm on $H^1_0$.  Specifying $\alpha > 0$ does not change the results dramatically; however, it does appear to improve conditioning of $\bs{A}$.}, and $w(x)$ is some smoothly varying positive weighting function.  Specifically, we require $\LRb{w(x)}$ to be of magnitude $O(\epsilon)$ for $x\in \Gamma_{\rm in}$, but $O(1)$ away from the inflow boundary.\footnote{Specific restrictions on $w$ are derived in \cite{DPGrobustness} in context of the DPG method.}

@@

\begin{remark}
We remark that this inclusion of $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ is a variational crime under the assumption that $u \in H^1_0(\Omega)$; the proper way to include such a term in a conforming manner (without introducing additional regularity assumptions on $u$) would be to introduce $\epsilon \pd{u}{n}$ as an additional unknown on the boundary, similar to the work done using DPG under the ultra-weak formulation \cite{DPG2,analysisDPG}.  However, we have found that doing so does not remove the boundary layer in the residual at the inflow, and numerical results appear to degenerate in quality as $\epsilon$ grows smaller and smaller.  We believe this is due to the fact that, by decoupling $\epsilon \pd{u}{n}$ as an additional unknown, the orthogonality boundary condition $\int_{\Gamma_{\rm in}} \pd{u}{n} e = 0$ is decoupled from the interior integrals and enforced strongly.\footnote{The same situation occurs when $\pd{u}{n}$ is declared as an additional unknown and when $\epsilon > 0$.}

We note that Broersen and Stevenson have also achieved good results by making use of the space $H^1_{\rm out}(\Omega)$ in their application of the DPG method to the mixed mild-weak formulation for convection-diffusion \cite{broersenStevenson}.  The mild-weak formulation effectively enforces the orthogonality of $e$ to polynomials of lower order on $\Gamma_{\rm in}$ in a conforming manner, by introducing an additional flux unknown representing $\epsilon \pd{u}{n}$.

%For many flow problems, activity near the inflow is typically very smooth and can thus be represented using a minimal number of elements under an effective adaptive mesh refinement scheme, implying that the cost of introducing such additional unknowns on $\Gamma_{\rm in}$ can be minimized.  However, since the codebase we currently use does not feature unknowns with support only on element edges/faces, we continue to operate under this variational crime, in hopes that we can implement a conforming version in the near future.  %Another way to properly include the term $\epsilon \pd{u}{n}$ in the variational formulation would be to work with higher continuity trial spaces that admit a normal trace of the derivative on the boundary \cite{nurbsTrace, NURBSorig}.  
\end{remark}
\begin{remark}
Various other methods of implementing a weak boundary condition on $e$ at the inflow $\Gamma_{\rm in}$ were implemented; for example, the inner product $\LRp{e,v}_V$ was modified by adding the a weak penalization term $$\epsilon C(h,p+\triangle p)\int_{\Gamma_{\rm in}}ev $$ to enforce the boundary condition at $\left.e\right |_{\Gamma_{\rm in}}$, where $C(h,p+\triangle p) = p^2/h$, which is a common choice of penalization parameter in high order finite element literature \cite{nurbsTrace,Warburton20032765}. However, the inclusion of the nonconforming term $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ in the bilinear form still resulted in the best solutions for all our numerical tests.  
\end{remark}

>>>>

@@

Our starting point is the minimization of some measure of error over a finite-dimensional space.  We begin by first introducing an abstract variational formulation 
\begin{equation}
\eqnlab{variationEq}
\left\{
  \begin{array}{l}
    \text{Given } l \in V', \text{ find } u \in U  \text{ such that} \\ 
    b(u,v) = l(v), \quad \forall v\in V,
  \end{array}
  \right.
\end{equation}
where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous bilinear form.  Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.  Throughout the paper, we suppose the variational problem \eqnref{variationEq} to be well-posed in the inf-sup sense. We can then identify a unique operator $B:U\rightarrow V'$ such that 
\[
\langle Bu,v\rangle_{V' \times V} \coloneqq b(u,v), \quad u\in U, v\in V
\]
with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the our variational problem
\begin{equation}
\eqnlab{dualEq}
Bu = l \quad \text{in } V'.
\end{equation}
We are interested in minimizing the residual over the discrete approximating subspace $U_h \subset U$
\[
u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h) \coloneqq \frac{1}{2}\|l-Bu_h\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| l(v)- b(u_h,v)|^2}{\nor{v}_V^2}.
\]
For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.  If we define the problem-dependent \textit{energy norm} 
\[
\nor{u}_E \coloneqq \nor{Bu}_{V'},
\]
then we can equate the minimization of $J(u_h)$ with the minimization of error in $\nor{\cdot}_E$.

The first order optimality condition for minimization of the quadratic functional $J(u_h)$ requires the G\^ateaux derivative to be zero in all directions $\delta u \in U_h$,
\begin{align}
\left(l-Bu_h,B\delta u\right)_{V'} = 0, \quad \forall \delta u \in U,
\label{orthog}
\end{align}
which is nothing more than the least-squares condition enforcing orthogonality of error with respect to the inner product on $V$.

The difficulty in working with the first-order optimality condition~\eqref{orthog} is that the inner product $\LRp{\cdot,\cdot}_{V'}$ cannot be evaluated explicitly.  However, we have that 
\begin{align}
\left(l-Bu_h,B\delta u\right)_{V'} = \left(R_V^{-1}(l-Bu_h),R_V^{-1}B\delta u\right)_{V},
\label{rieszOrthog}
\end{align}
where $R_V: V\rightarrow V'$ is the Riesz map mapping elements of a Hilbert space $V$ to elements of the dual $V'$ defined by
\[
\LRa{R_Vv,\delta v}_{V\times V'} \coloneqq \LRp{v,\delta v}_V.
\]
Furthermore, the Riesz operator is an isometry, such that $J(u_h) = \frac{1}{2}\nor{l-Bu_h}^2_{V'} = \frac{1}{2}\nor{R_V^{-1}(l-Bu_h)}^2_{V}$.  Thus, satisfaction of~\eqref{rieszOrthog} is exactly equivalent to satisfaction of the original optimality conditions~\eqref{orthog}.

@@

Secondly, we need to enforce the orthogonality of the error in equation~\eqref{rieszOrthog}, which becomes
\begin{align*}
\LRp{e,R_V^{-1}B\delta u}_V &= 0, \quad \forall \delta u \in U_h\\
\Rightarrow \LRa{e,B\delta u}_{V\times V'} &= b(\delta u, e) = 0.
\end{align*}
Putting these two conditions returns the symmetric saddle-point problem for $\LRp{e,u_h} \in V\times U_h$
\begin{align*}
\LRp{e,v}_V + b(u_h,v) &= l(v), \quad \forall v\in V\\
b(\delta u, e) &= 0, \quad \forall \delta u \in U_h.
\end{align*}
We note that, under the perspective of the minimization of $J(u_h)$, this system can be viewed as a constrained optimization problem for $e$, where $u_h$ are Lagrange multipliers enforcing satisfaction of the variational problem.

@@

This formulation was first introduced by Dahmen et al.\ in \cite{DahmenVariationalStabilization}, where $V_h$ was determined adaptively.  The method proceeded in two steps -- first, $V_h$ was set equal to $U_h$ on what we will define as the \textit{coarse mesh}.  Next, \textit{a posteriori} error estimators for $e$ (based on a specific choice of inner product $\LRp{\cdot,\cdot}_V$) were used to drive adaptivity to determine a fine-scale mesh on which $V_h$ was supported.  We choose a simpler representation -- if $U_h$ is represented by polynomials of order $p$, we set $V_h = P^{p+\triangle p}$ globally.  We note that these two choices of discretization for $V$ are not mutually exclusive, and that novel choices for $V_h$ are likely the key to yielding computationally effective methods under this framework.  
\subsection{DPG optimal test function framework}

The DPG method was introduced by Demkowicz and Gopalakrishnan in 2009, and rapidly applied to a series of problems in computational mechanics \cite{DPG2,DPG3,DPG4,maxwellDPG,stokesDPG}.  Though the DPG method shares the same variational setting as Dahmen et al.\, each method followed very different approaches in implementation.  Recall the orthogonality of error~\eqref{rieszOrthog}; by defining the error representation function $e$ and undoing the Riesz map acting on $B\delta u$, we recovered a saddle point formulation.  However, it is possible to instead undo the Riesz map acting on the residual instead, to recover
\begin{align*}
\LRp{R_V^{-1}\LRp{l-Bu_h},R_V^{-1}B\delta u}_V &= 0, \quad \forall \delta u \in U_h\\
\Rightarrow \LRa{\LRp{l-Bu_h},R_V^{-1}B\delta u}_{V\times V'} &= 0\\
\Rightarrow l\LRp{R_V^{-1}B\delta u}-b\LRp{u_h,R_V^{-1}B\delta u} &= 0
\end{align*}
If we define $v_{\delta u} \coloneqq R_V^{-1}B\delta u$, then we recover the original variational formulation with a nonstandard test space
\[
b(u_h,v_{\delta u}) = l(v_{\delta u}), \quad \forall \delta u \in U_h.
\]
The DPG method with optimal test functions was constructed under this perspective of minimization of $J(u_h)$.  While $v_{\delta u} \in V$ must still be solved for approximately, under the assumption of discontinuous test functions, this solve can be localized to a single element.\footnote{In practice, if $U_h(K) = P^p(K)$ is the space of polynomials of order $p$ over the element $K$, then the enriched space $V_h \subset V$ is chosen to be $V_h(K) = P^{p+\triangle p}(K)$, where $\triangle p \geq n$, and $d$ is the spatial dimension.}

@@

We begin again with the variational problem
\[
\LRa{Bu,v}_{V'\times V} = \LRa{l,v}_{V'\times V},
\]
where, as before, $B: U\rightarrow V'$ is the operator form of $b(u,v)$, and $l \in V'$ is the load.  Standard VMS techniques then decompose $U$ into a \textit{coarse scale} space $U_h$ and \textit{fine scale} space $U'$, such that the coarse and fine scales $u_h \in U_h \subset U$ and $u' \in U'$ are related through some yet-unspecified orthogonality condition.  Decomposing $u = u_h + u'$ gives 
\begin{align*}
u_h \in U_h, u' \in U\setminus U_h, v \in V\\
\LRa{Bu_h,v}_{V'\times V} + \LRa{Bu',v}_{V'\times V} = \LRa{l,v}_{V'\times V}
\end{align*}
We can now explicitly choose our orthogonality condition defining the fine scales and rewrite the above problem as 
\begin{align*}
u_h \in U_h, u' \in U, v \in V\\
\LRa{Bu_h,v}_{V'\times V} + \LRa{Bu',v}_{V'\times V} &= \LRa{l,v}_{V'\times V}\\
\LRp{u',\bar{w}}_E &= 0, \quad \forall \bar{w} \in U_h,
\end{align*}
where $\LRp{u',\bar{w}}_E$ is defined through
\begin{align*}
\LRp{u',\bar{w}}_E = \LRp{Tu',T\bar{w}}_V\\
T:U\rightarrow V, \quad T \coloneqq R_V^{-1} B
\end{align*}
where $\LRp{v,\delta v}_V$ is an inner product on $V$ and $R_V$ is the Riesz map associated with this inner product.  DPG literature refer to $T$ as the \textit{trial-to-test} operator, which, given a basis function $\phi_i \in U_h$, returns the optimal test function for $\phi_i$ \cite{DPG2}.

If we define our fine-scale using the above orthogonality condition, we have that
\begin{align*}
\LRp{Tu',v}_V = \LRp{R_V^{-1}Bu',v}_V = \LRa{Bu',v}_{V'\times V}\\
\LRp{u',\bar{w}}_E = \LRp{Tu',R_V^{-1}B\bar{w}}_V = \LRa{Tu',B\bar{w}}_{V\times V'}
\end{align*}
and can now rewrite our above VMS formulation as 
\begin{align*}
u_h \in U_h, u' \in U, v \in V\\
\LRa{Bu_h,v}_{V'\times V} + \LRp{Tu',v}_{V} &= \LRa{l,v}_{V'\times V}\\
\LRp{Tu',B\bar{w}}_{V\times V'} &= 0, \quad \forall \bar{w} \in U_h.
\end{align*}
The saddle point formulation of Section~\ref{sec:saddlePoint} can be interpreted as solving not for $u'$, but for $e\coloneqq Tu'$.  The discrete approximation then follows directly from setting $V \coloneqq V_h$, some finite-dimensional enriched space, which impacts the method only through the approximation of $Tu'$ and the construction of the Riesz map $R_V^{-1}$.

To summarize, the minimum-residual framework motivating both Dahmen's variational stabilization and Demkowicz's DPG method can be characterized as a VMS method under which 
\begin{itemize}
\item Orthogonality of $U_h$ and $U'$ is defined through a nonstandard \textit{energy inner product} (i.\ e.\ $\LRp{u',u_h}_E = 0$), and
\item A change of variables (i.\ e.\ solving for $Tu'$ instead of $u'$) symmetrizes the fine-scale contribution and overall system.
\end{itemize}

@@

Our first method is motivated by previous results for the DPG method in \cite{DPGrobustness}, which achieved good results through a modification of the test norm.  We set
\[
\nor{v}_{V,w}^2 \coloneqq \frac{L}{\LRb{\beta}}\nor{\sqrt{w}\beta\cdot \Grad v}_{\L}^2 + \epsilon\nor{\Grad v}_{\L}^2 + \alpha\nor{v}_{\L}^2,
\]
where $L = \LRb{\Omega}^{\frac{1}{d}}$ is the length measure of $\Omega$ in $d$ spatial dimensions, $\LRb{\beta} = \max_\Omega \nor{\beta}_{l^2}$, and we have introduced the scaling $\frac{L}{\LRb{\beta}}$ on the streamline diffusion term for unit consistency\footnote{In all problems considered, $\frac{L}{\LRb{\beta}} = O(1)$.}. $\alpha \geq 0$ is a user-specified constant with units of inverse time\footnote{In the case where $\alpha = 0$, the seminorm remains a norm due to equivalence with the $H^1$ seminorm, which is norm on $H^1_0$.  Specifying $\alpha > 0$ does not change the results dramatically; however, it does appear to improve conditioning of $\bs{A}$.}, and $w(x)$ is some smoothly varying positive weighting function.  Specifically, we require $\LRb{w(x)}$ to be of magnitude $O(\epsilon)$ for $x\in \Gamma_{\rm in}$, but $O(1)$ away from the inflow boundary.  Specific restrictions on $w$ are derived in \cite{DPGrobustness} in context of the DPG method.

@@

\begin{remark}
We remark that this inclusion of $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ is a variational crime under the assumption that $u \in H^1_0(\Omega)$; the proper way to include such a term in a conforming manner (without introducing additional regularity assumptions on $u$) would be to introduce $\epsilon \pd{u}{n}$ as an additional unknown on the boundary, similar to the work done using DPG under the ultra-weak formulation \cite{DPG2,analysisDPG}.  We note that Broersen and Stevenson have also achieved good results by making use of the space $H^1_{\rm out}(\Omega)$ in their application of the DPG method to the mixed mild-weak formulation for convection-diffusion \cite{broersenStevenson}.  The mild-weak formulation effectively enforces the orthogonality of $e$ to polynomials of lower order on $\Gamma_{\rm in}$ in a conforming manner, by introducing an additional flux unknown representing $\epsilon \pd{u}{n}$.

For many flow problems, activity near the inflow is typically very smooth and can thus be represented using a minimal number of elements under an effective adaptive mesh refinement scheme, implying that the cost of introducing such additional unknowns on $\Gamma_{\rm in}$ can be minimized.  However, since the codebase we currently use does not support unknowns with support only on element edges/faces, we continue to operate under this variational crime, in hopes that we can implement a conforming version in the near future.  Another way to properly include the term $\epsilon \pd{u}{n}$ in the variational formulation would be to work with higher continuity trial spaces that admit a normal trace of the derivative on the boundary \cite{nurbsTrace, NURBSorig}.  
\end{remark}
\begin{remark}
Various other methods of implementing a weak boundary condition on $e$ at the inflow $\Gamma_{\rm in}$ were implemented; for example, the inner product $\LRp{e,v}_V$ was modified by adding the a weak penalization term $$\epsilon C(h,p+\triangle p)\int_{\Gamma_{\rm in}}ev $$ to enforce the boundary condition at $\left.e\right |_{\Gamma_{\rm in}}$, where $C(h,p+\triangle p) = p^2/h$, which is a common choice of penalization parameter in high order finite element literature \cite{nurbsTrace,Warburton20032765}. However, the inclusion of the nonconforming term $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ in the bilinear form still resulted in the best solutions for all our numerical tests.  
\end{remark}
